The error when inferring phylogenies with incipient species by a Birth-Death model

### 2018-04-05 article.tex
Can create PDF

% Affiliations
\usepackage{authblk}
\title{Stage 1 Registered Report: The error when inferring phylogenies with incipient species by a Birth-Death model}
% \subtitle{Should protracted speciation be incorporated in phylogenetic tree construction methods?}

@@

We predict that nLTT statistic values increase 
with an increasing protractednedness (that is, a low speciation completion rate),
but we cannot predict the the extent of this error, as it has never been 
measured [NOTE: this may be easy to change: Etienne & Rosindel 2012 show the equations
for the expected number of lineages through time. I think I may be able to pull
of a prediction here, by fitting a BD curve on a PBD curve with a minimized error,
but research would be needed to investigate that].

@@

\begin{figure}[]
  \includegraphics[width=0.9\textwidth]{fig_does_sampling_matter.png}
\end{figure}

\begin{figure}[]
  \includegraphics[width=0.9\textwidth]{fig_does_protractedness_matter.png}
\end{figure}

@@

\begin{itemize}  
  \item 12 simulation parameters:
  \begin{enumerate}  
    \item speciation initiation rate
    \item speciation completion rate
    \item extinction rate
    \item crown age
    \item crown age sigma
    \item sampling method
    \item mutation rate
    \item sequence length
    \item mcmc length
    \item tree sim rng seed
    \item alignment rng seed
    \item beast2 rnd seed
  \end{enumerate}
  \item [NOTE: add yes/no?] expected speciation completion time (from Etienne & Rosindell 2012)
  \item [NOTE: add yes/no?] expected duration of speciation (from Etienne & Rosindell 2012)
  \item number of taxa in incipient species tree (also: number of subspecies)
  \item [NOTE: add yes/no?] would there be a difference in brach lengths between the two sampling methods?
  \item number of taxa in species tree (also: number of species)
  \item mean nLTT statistic
  \item median nLTT statistic
  \item lower bound of 95\% HPD value of nLTT statistic
  \item upper bound of 95\% HPD value of nLTT statistic
  \item 11 ESSes of all parameters estimated by BEAST2:
  \begin{enumerate}  
    \item posterior
    \item likelihood 
    \item prior 
    \item treeLikelihood 
    \item TreeHeight 
    \item BirthDeath 
    \item BDBirthRate 
    \item BDDeathRate 
    \item logP.mrca 
    \item mrcatime 
    \item clockRate
  \end{enumerate}
  \item [some] MCMC operator acceptances
\end{itemize}

>>>>

% Affiliations
\usepackage{authblk}
\title{The error when inferring phylogenies with incipient species by a Birth-Death model}
% \subtitle{Should protracted speciation be incorporated in phylogenetic tree construction methods?}

@@

We predict that nLTT statistic values increase 
with an increasing protractednedness (that is, a low speciation completion rate),
but we cannot predict the the extent of this error, as it has never been 
measured [NOTE: this may be easy to change: Etienne \& Rosindel 2012 show the equations
for the expected number of lineages through time. I think I may be able to pull
of a prediction here, by fitting a BD curve on a PBD curve with a minimized error,
but research would be needed to investigate that].

@@

@@

\begin{itemize}  
  \item 12 simulation parameters:
  \begin{enumerate}  
    \item speciation initiation rate
    \item speciation completion rate
    \item extinction rate
    \item crown age
    \item crown age sigma
    \item sampling method
    \item mutation rate
    \item sequence length
    \item mcmc length
    \item tree sim rng seed
    \item alignment rng seed
    \item beast2 rnd seed
  \end{enumerate}
  \item [NOTE: add yes/no?] expected speciation completion time (from Etienne \& Rosindell 2012)
  \item [NOTE: add yes/no?] expected duration of speciation (from Etienne \& Rosindell 2012)
  \item number of taxa in incipient species tree (also: number of subspecies)
  \item [NOTE: add yes/no?] would there be a difference in brach lengths between the two sampling methods?
  \item number of taxa in species tree (also: number of species)
  \item mean nLTT statistic
  \item median nLTT statistic
  \item lower bound of 95\% HPD value of nLTT statistic
  \item upper bound of 95\% HPD value of nLTT statistic
  \item 11 ESSes of all parameters estimated by BEAST2:
  \begin{enumerate}  
    \item posterior
    \item likelihood 
    \item prior 
    \item treeLikelihood 
    \item TreeHeight 
    \item BirthDeath 
    \item BDBirthRate 
    \item BDDeathRate 
    \item logP.mrca 
    \item mrcatime 
    \item clockRate
  \end{enumerate}
  \item [some] MCMC operator acceptances
\end{itemize}
